---
title: "Week 3 - Cincinnati Weather Analysis"
author: "Nidhi-M"
date: "October 29, 2016"
output: html_document
---

## Synopsis

Analysis of Temperature for days in all the months for years from 1995 to present is done in this document.  
1. It is found that a lot of variation in temperature is seen in months for January anf February for over years  
2. Year 1996 & 2014 has seen most extreme temperature on the lower end while Years 1997 & 2012 has seen extremes in Upper end

## Packages Required & Data Collection

```{r message=FALSE}
library(ggplot2)
library(knitr)
Weather <- read.table("http://academic.udayton.edu/kissock/http/Weather/gsod95-current/OHCINCIN.txt", col.names = c("Month","Day", "Year", "Temperature")) ## Try using Read_table and read_fwfq
```
## Source Code
The Data contains Temperature for Cincinnati, Ohio for every day in a month from 1995 to 2016.
Text file downloaded is present [here](http://academic.udayton.edu/kissock/http/Weather/gsod95-current/OHCINCIN.txt).
Columns include Month, Day, Year and Temperature in Fahrenheit

## Data Description


```{r}
colnames(Weather); 
nrow(Weather)
str(Weather)
Weather[Weather$Temperature == -99, 4] <-  NA
sum(is.na(Weather$Temperature)) ##which to see any patterns in the indexes of the missing value
summary(Weather)

```


## Data Visualization {.tabset}

### Monthly Analysis
```{r warning=FALSE}
ggplot(data = Weather) +
  geom_point(mapping = aes(x = Day, y = Temperature )) +
  facet_grid(. ~ Month) + 
  ylab("Temperature in Fahrenheit")  +
  labs(title = "Monthly trend and Variation over years")
##Replace the NA with with mean of 3 days after and before day, why 3 as there were 2 consecutive days missing
## mention what have done with the missing values 
##Hmiec package descibe
## ggplot works well with date string
## get the unique values
##table fror the years , month
## Convert it to categorical value
##Luber day package for dates
##month.abb

##factor(monthabb[temp_df$Month], levels = month.abb)
##order will the index and sort will give the valus 
##ggplot
##Heat map
##compare with otger city
##jitter
```
      
      
### Yearly Anlaysis
```{r}
boxplot(Temperature~Year,
        data=Weather,
        main="Temperature Yearly Plot", 
        xlab="Years", ylab="Temperature in Fahrenheit")

```
    

### Averages
```{r}
MeanMonthlyTemperature <- aggregate( x=Weather, 
                                     by = list( Weather$Year ,Weather$Month), 
                                     FUN = mean, na.rm=TRUE)
colors <- rainbow(22)
Years <- 1995:2016
plot(MeanMonthlyTemperature[MeanMonthlyTemperature$Year == 1995, 6],
     type = "l",
     col = colors[1] , 
     xlab = "Month", 
     ylab = "Average Temperature in Fahrenheit", 
     main = "Average trends for months over year")
for ( i in 2:22)
  lines(MeanMonthlyTemperature[MeanMonthlyTemperature$Year == Years[i], 6],type = "l",col = colors[i])
#legend("bottom", legend = c("1995","1996", 1997:2016),  col = rainbow(22) )
```









