---
title: "Week1-Markdown"
author: "Nidhi-M"
date: "October 14, 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

   
     
     
###About Me 

I was born and brought up in Bombay (Mumbai). After completing Engineering from V.J.T.I., I worked at CitiusTech as a Software Engineer for 2 years, majorly working on MS-SQL, Elasticsearch for helping various projects for performance optimization on an application by analyzing humongous data. An inclination to learn more about tools and tactics used to derive answers from data, motivated me to pursue career in Analytics. In order to come out of comfort zone both personally and proffessionaly I accepted an admission to MS in Business Analytics program from the University of Cincinnati. 
  
  
#####Some R-code is attached as second part of the assignment
```{r}
a <- 100*(1+ (0.05/12)**24)
print(a)

b <- 3333/222
print(b)
```
At higher value of n, the equation $(1 + \frac{1}{n} )^{n}$ remains constant

```{r}
vector <- seq( 10000000,.Machine$integer.max, by=10000000)
c <- (1+1/vector)**vector
head(c)
tail(c)
```
#####Calculating the Economic Order Quantity (EOQ) at annual demand of 1000, fixed cost of 5 per order and 0.25 as holding cost 
```{r}
D <-  1000;K <- 5;h <- 0.25;Q <- sqrt(2*D*K/h)
print(Q)
```
  
  
#####Calculating the final value of the deposit, whose principle amount is 100, at rate of 0.08 for 3 years with 12 payments every year
```{r}
P <- 100;r <- 0.08;n <- 12;t <- 3;
F <- P*((1+(r/n))**(n*t))
print(F)
```

