---
title: "Week1-Markdown"
author: "Nidhi-M"
date: "October 14, 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

   
     
     
###About Me 

Born and brought up in Bombay. After completing Engineering from V.J.T.I., I worked at CitiusTech as a Software Engineer for 2 years. An inclination to learn more about tools and tactics used to derive answers from data, motivated me to pursue MS in Business Analytics from the University of Cincinnati. I took up Data Science Specialization offered on Coursera, where I got introduced to R. Have majorly worked on ELK stack and  MS-SQL 
  
  
#####Some R-code is attached as second part of the assignment
```{r}
a <- 100*(1+ (0.05/12)**24)
print(a)

b <- 3333/222
print(b)
```
At higher value of n, the equation (1 + $\frac(1}{n}$)^{n} remains constant
```{r}
i <- 1; d <- list()
for (n in seq( 10000000,.Machine$integer.max, by=10000000))
{
  c <- (1+1/n)**n
  ##cat(sprintf("%f -  %f \n", c , n))
  d[[i]] <-  (1+1/n)**n
  i = i+1
}
head(d)
tail(d)
```
#####Calculating the Economic Order Quantity (EOQ) at annual demand of 1000, fixed cost of 5 per order and 0.25 as holding cost 
```{r}
D <-  1000;K <- 5;h <- 0.25;Q <- sqrt(2*D*K/h)
print(Q)
```
  
  
#####Calculating the final value of the deposit, whose principle amount is 100, at rate of 0.08 for 3 years with 12 payments every year
```{r}
P <- 100;r <- 0.08;n <- 12;t <- 3;
F <- P*((1+(r/n))**(n*t))
print(F)
```

